Dependently Typed Multi-stage Calculus

### 2019-11-22 slides/main.tex
Fix bugs.

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm enables that
    \begin{itemize}
        \item Generation of code at runtime
        \item Evaluation of code at runtime
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using runtime information
    \end{itemize}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using normal values in code values
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul3}}_{\text{normal value}}\ x = 2 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul3}\ 5)}_{\text{code value}} \)
    \end{center}
    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
\end{frame}

@@

\begin{frame}[fragile]{vadd-gen in \LMD}
    Type tells us the length of vector.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vt}{\text{Vec}\ \%3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I \to \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
        \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
        \> \( \text{val}\ \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\[2mm]
    \end{tabbing}
    Now, vadd3 takes only vectors of length 3.
    \note{
        vadd-gen is changed as follows in \LMD.
        Thanks to dependent types ...
    }
\end{frame}

@@

\begin{frame}[fragile]{Solution}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    Introduce \QPercent.
    \begin{center}
        \infrule[{\QPercent}]{
            M \text{ is a closed term.}
        }{
            \G\vdash \%_\alpha M \E M
        }
    \end{center}
    Erase the symbol of \( \% \) under the condition.
    \begin{itemize}
        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\
            \hspace{15mm} \( (\E  \TW (\Vpt \to \Vpt \to \Vpt)) \)
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Conclusion}
    We introduced dependent types into multi-stage programming.
    \begin{itemize}
        \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
            \item Define equality rules.
                \begin{itemize}
                        \item Especially, dealing with CSP.
                \end{itemize}
            \item Prove type soundness.
        \end{itemize}
    \note{
    }
\end{frame}

>>>>

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm that enables
    \begin{itemize}
        \item Generation of code at runtime
        \item Evaluation of code at runtime
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using runtime information
    \end{itemize}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using normal values in code values
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{normal value}}\ x = 5 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul5}\ 4)}_{\text{code value}} \)
    \end{center}
    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
\end{frame}

@@

\begin{frame}[fragile]{vadd-gen in \LMD}
    Type tells us the length of vector.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vt}{\text{Vec}\ \%3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{vadd-gen} : \Pi n:\I. \TW (\Vn \to \Vn \to \Vn) \) \\[2mm]
        \> \( \textbf{let}\ \text{vadd3} = \text{vadd-gen}\ 3;; \) \\
        \> \( \text{val}\ \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\[2mm]
    \end{tabbing}
    Now, vadd3 takes only vectors of length 3.
    \note{
        vadd-gen is changed as follows in \LMD.
        Thanks to dependent types ...
    }
\end{frame}

@@

\begin{frame}[fragile]{Solution}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    Introduce \QPercent.
    \begin{center}
        \infrule[{\QPercent}]{
            M \text{ is a closed term.}
        }{
            \G\vdash \% M \E M
        }
    \end{center}
    Erase the symbol of \( \% \) under the condition.
    \begin{itemize}
        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\
            \hspace{15mm} \( (\E  \TW (\Vpt \to \Vpt \to \Vpt)) \)
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Conclusion}
    We introduced dependent types into multi-stage calculus.
    \begin{itemize}
        \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
            \item Define equality rules.
                \begin{itemize}
                        \item Especially, dealing with CSP.
                \end{itemize}
            \item Prove type soundness.
        \end{itemize}
    \note{
    }
\end{frame}
